Offshore Blue Crab Densities for <br/> The Gulf of Mexico

### 2020-01-27 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
manuscript plot updates

#Format ggplot for rest of document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), 
                             panel.grid.minor = element_blank(), 
                             panel.border = element_rect(fill = NA)))

@@

```{r}
seamap <- seamap %>% rename_all(tolower)
seamap_west <- seamap %>% 
  filter(statzone != 12,
         statzone %in% 11:21) %>% 
  mutate(statzone = factor(statzone))

@@

@@

```{r}
seamap_west %>% 
  mutate(year = as.numeric(as.character(year_f))) %>% 
  filter(cpue_towspd > 0) %>% 
  ggplot(aes(year, cpue_towspd)) +
  #geom_boxplot(aes(group = year)) +
  geom_boxplot(aes(group = year), outlier.shape = NA) +
  ylim(0, 2) +
  labs(x = NULL, y = "Crabs / Hectare")
```

@@

```{r}
region_plot_west <- seamap_west %>% 
  filter(cpue_towspd > 0) %>% 
  ggplot(aes(region, cpue_towspd)) +
  geom_boxplot(aes(fill = season), outlier.shape = NA) +
   scale_fill_grey(start = 0.3, end = 0.5) +
  ylim(0, 2) +
  labs(x = NULL, y = "Crabs / Hectare") + 
  theme(
    legend.title = element_blank(),
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA)
    )

season_plot_west <- seamap_west %>% 
    group_by(region, season) %>% 
    summarise(
      stations = n(),
      `missing obs`     = sum(is.na(cpue_towspd)),
      `% Occurrence` = mean(crab_presence, na.rm = T),
      `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(stations - `missing obs`)) %>% 
    mutate(
      occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
      occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
      occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
    ) %>% 
  ggplot(aes(region, `% Occurrence`)) +
    geom_pointrange(aes(ymin = occurrence_ymin, 
                        ymax = occurrence_ymax, 
                        shape = season, 
                        color = season)) +
    scale_color_grey(start = 0.3, end = 0.5) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    labs(x = NULL, y = "Percent Occurrence") + 
  theme(
    legend.title = element_blank(),
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA)
    )

region_plot_west + season_plot_west

@@

>>>>

#Format ggplot for rest of document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), 
                             panel.grid.minor = element_blank(), 
                             panel.border = element_rect(fill = NA),
                             axis.text = element_text(size = 12),
                             axis.title = element_text(size = 14)))

@@

```{r}
seamap <- seamap %>% rename_all(tolower) %>% filter(statzone != 12)
seamap_west <- seamap %>% 
  filter(statzone %in% 11:21) %>% 
  mutate(statzone = factor(statzone))

@@

The following numbers are from the Western Gulf Dataset used in the generalized linear model*

@@

*NOTE: Contains Data Across All Years and Regions (Including Florida)*

```{r}
year_sums <- seamap %>% 
  group_by(survey_year) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(cpue_towspd)),
            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
            `SD`              = sd(cpue_towspd, na.rm = T),
            `Var`             = var(cpue_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(crab_presence, na.rm = T),
            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
  ungroup() %>% 
    mutate(Survey_Year        = factor(survey_year),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

year_sums %>% select(`Survey Year` = survey_year, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()

year_plot <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `Mean Catch`)) +
    geom_errorbar(aes(x = survey_year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  labs(x = NULL,
       y = "Mean Catch (C. sapidus / Hectare)")

year_plot

year_foa <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `% Occurrence`)) +
    geom_errorbar(aes(x = survey_year, 
                      ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  size = .25) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL, y = "Percent Occurrence")

year_foa

year_plot + year_foa
```

@@

```{r}
rs_summary <- seamap %>% 
  filter(is.na(region)      == FALSE) %>% 
  group_by(region, season) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(cpue_towspd)),
            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
            `SD`              = sd(cpue_towspd, na.rm = T),
            `Var`             = var(cpue_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(crab_presence, na.rm = T),
            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
           region             = factor(region, 
                                       levels = c("Texas", "Louisiana", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
    )

#Summary Table
rs_summary %>% 
  select(Region = region, Season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% 
  knitr::kable()

# Plot
rs_plot <- rs_summary %>% 
  ggplot(aes(region, `Mean Catch`, fill = season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = "Mean Catch (C. sapidus / Hectare)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA))

rs_plot

rs_plot_2 <- rs_summary %>% 
  ggplot(aes(region, `% Occurrence`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA))

rs_plot + rs_plot_2

@@

```{r}
season_summary <- seamap %>% 
  group_by(survey_year, season) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(cpue_towspd)),
            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
            `SD`              = sd(cpue_towspd, na.rm = T),
            `Var`             = var(cpue_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(crab_presence, na.rm = T),
            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>% 
    ungroup() %>% 
    mutate(survey_year        = factor(survey_year),
           # StatZone         = factor(StatZone),
           # StatZone         = fct_rev(StatZone),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )

season_summary %>% select(`Survey Year` = survey_year, Season = season, Stations, `Missing Obs`, `% Occurrence`, `Mean Catch`, SD, Overdispersed) %>% knitr::kable()

season_plot <- season_summary %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot(aes(survey_year, `Mean Catch`, fill = season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = "Mean Catch (C. sapidus / Hectare)") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA))

season_plot

season_plot_2 <- season_summary %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot(aes(survey_year, `% Occurrence`, fill = season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = "Survey Year",
       y = "Percent Occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA))

season_plot + season_plot_2
```
